Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-09-30 reviews.Rmd
Update reviews.Rmd

We talk about the scientific procedures, of which a statistical test is a piece.

@@

The point of not using a Type 1 error rate is to differentiate the statistical test from the the researcher's scientific judgement.
Type 1 error rate is a property of a test under certain conditions.
Theoretical risk refers to the individual judgement of a researcher about the substantive hypothesis and the study design as a whole.

@@

No, we relate our work to beliefs we think are commonly held.
Researchers find the idea of a risky test appealing.
Popper gives one explanation for this appeal, but we happen to have a different view.

@@

As stated above, if Popper would happen to agree, we indeed would have to rethink our arguments.

@@

We appreciate this hard work.
Yet we believe that this is not the only useful perspective on the utility of preregistration.

@@

We take the criticism of the terminology seriously.
Although we have opted to stick with most of the terms as we defined them, we provided more references.
It might also be the case that the differences in philosophical traditions lead to some criticism.

>>>>

Please note that our framework adressess the entire scientific procedure, of which a statistical test is only one piece.
It would cost our framework its generality if we reduced 'theoretical risk' to only a property of the statistical test (such as severity).

@@

This concern is conceptually very similar to the second-to-last concern.
The point of not using a Type 1 error rate is to differentiate the statistical test from the the researcher's scientific judgement.
Type 1 error rate is a property of a test under certain conditions.
Theoretical risk refers to the individual judgement of a researcher about the substantive hypothesis and the study design as a whole.

@@

No, we relate our work to beliefs we think are commonly held.
Researchers find the idea of a risky test appealing.
Popper gives one explanation for this appeal, but we happen to adopt a different philosophical view here.

@@

As stated above, if Popper happened to agree, we indeed would have to rethink our arguments.

@@

We appreciate this important work.
Yet we believe that this is not the only useful perspective on the utility of preregistration.

@@

We take the criticism of the terminology seriously.
We have opted to stick with most of the terms as we defined them initially, as we did with good reasons, we now back them up with additional references.
